---
title: "Visual representation of Lipinski's descriptors"
author: Saw Simeon, Nuttapat Anuwongcharoen, Watshara Shoombuatong, Aijaz Ahmad Malik,
  Virapong Prachayasittikul, Jarl E. S. Wikberg and Chanin Nantasenamat
date: "June 7, 2016"
output: pdf_document
---

## Chemical space of AChE inhibitors
Convert IC50 to pIC50 as well as binning the activity (i.e., Active, Inactive and Intermediate)

```{r}
data <- read.csv("Lipinski_descriptors.csv")
IC50_nm <- data$STANDARD_VALUE
IC50 <- as.numeric(IC50_nm)*10^-9
pIC50 <- -log10(IC50)
descriptors_name <- c("ALogP", "nHBAcc", "nHBDon", "MW")
descriptors <- data[, descriptors_name]
#data_classification <- cbind(pIC50, descriptors)
Activity <- ifelse(pIC50 > 6, "Active",
                      ifelse((pIC50 <= 6) & (pIC50 < 5), "Inactive", 
                             "Intermediate"))
Activity <- data.frame(Activity)

```

\pagebreak

## Visualization of Lipinski's descriptors

### Chemical space of AChE inhibitors are shown as active (green), inactive (red) and intermediate (blue)

```{r, warning= FALSE, message=FALSE}
library(ggplot2)
library(cowplot)
data_2 <- cbind(Activity, descriptors)
data_2 <- na.omit(data_2)
data_plot <- data.frame(data_2)
p <- ggplot(data_plot, aes(MW, ALogP))
p <- p + geom_point(aes(colour = factor(Activity)), size = 3, alpha = 0.3)
p <- p + theme(legend.position = ("none"),
           panel.border = element_rect(linetype = "solid",
                                       colour = "black", fill = NA, size = 1),
           axis.text.x = element_text(colour = "black", size = 10),
           axis.text.y = element_text(colour = "black", size = 10),
           plot.margin = unit(c(1, 1, 1, 1), "cm"),
           axis.title.x = element_text(colour = "black", size = 15, face = "bold"),
           axis.title.y = element_text(colour = "black", size = 15, face = "bold")
           )
print(p)
```

\pagebreak

### Boxplot of Lipinski's rule-of-five descriptors (ALogP) 

```{r, warning= FALSE, message=FALSE}

p_1 <- ggplot(data_plot, aes(factor(Activity), ALogP))
p_1 <- p_1 + geom_boxplot(aes(fill = factor(Activity)), alpha = 0.7)
p_1 <- p_1 + theme(legend.position = ("none"),
                   panel.border = element_rect(linetype = "solid",
                                               colour = "black", fill = NA, size = 1),
                   axis.text.x = element_text(colour = "black", size = 15),
                   axis.text.y = element_text(colour = "black", size = 15),
                   plot.margin = unit(c(1, 1, 1, 1), "cm"),
                   axis.title.y = element_text(size = 20, face = "bold"),
                   axis.title.x = element_blank())

print(p_1)
```

\pagebreak

### Boxplot of Lipinski's rule-of-five descriptors (nHBAcc) 

```{r, warning= FALSE, message=FALSE}

p_2 <- ggplot(data_plot, aes(factor(Activity), nHBAcc))
p_2 <- p_2 + geom_boxplot(aes(fill = factor(Activity)), alpha = 0.7)
p_2 <- p_2 + theme(legend.position = ("none"),
                   panel.border = element_rect(linetype = "solid",
                                               colour = "black", fill = NA, size = 1),
                   axis.text.x = element_text(colour = "black", size = 15),
                   axis.text.y = element_text(colour = "black", size = 15),
                   plot.margin = unit(c(1, 1, 1, 1), "cm"),
                   axis.title.y = element_text(size = 20, face = "bold"),
                   axis.title.x = element_blank())
print(p_2)
```

\pagebreak

### Boxplot of Lipinski's rule-of-five descriptors (nHBDon) 

```{r, warning= FALSE, message=FALSE}

p_3 <- ggplot(data_plot, aes(factor(Activity), nHBDon))
p_3 <- p_3 + geom_boxplot(aes(fill = factor(Activity)), alpha = 0.7)
p_3 <- p_3 + theme(legend.position = ("none"),
                   panel.border = element_rect(linetype = "solid",
                                               colour = "black", fill = NA, size = 1),
                   axis.text.x = element_text(colour = "black", size = 15),
                   axis.text.y = element_text(colour = "black", size = 15),
                   plot.margin = unit(c(1, 1, 1, 1), "cm"),
                   axis.title.y = element_text(size = 20, face = "bold"),
                   axis.title.x = element_blank())
print(p_3)
```

\pagebreak

### Boxplot of Lipinski's rule-of-five descriptors (MW) 

```{r, warning= FALSE, message=FALSE}


p_4 <- ggplot(data_plot, aes(factor(Activity), MW))
p_4 <- p_4 + geom_boxplot(aes(fill = factor(Activity)), alpha = 0.7)
p_4 <- p_4 + theme(legend.position = ("none"),
                   panel.border = element_rect(linetype = "solid",
                                               colour = "black", fill = NA, size = 1),
                   axis.text.x = element_text(colour = "black", size = 15),
                   axis.text.y = element_text(colour = "black", size = 15),
                   plot.margin = unit(c(1, 1, 1, 0.4), "cm"),
                   axis.title.y = element_text(size = 20, face = "bold"),
                   axis.title.x = element_blank()) 

print(p_4)
```

\pagebreak

# Arranging boxplot of Lipinski's rule-of-file descriptors (ALogP, nHBAcc, nHBDon, MW)
```{r, fig.width = 10, fig.height= 10, warning=FALSE, message=FALSE}
library(cowplot)
plot_grid(p_1, p_2, p_3, p_4)

```
